---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# much_<span style="color:red;">f</span><span style="color:orange;">l</span><span style="color:gold;">u</span><span style="color:green;">o</span><span style="color:blue;">r</span><span style="color:indigo;">e</span><span style="color:violet;">s</span><span style="color:red;">c</span><span style="color:orange;">e</span><span style="color:green;">n</span><span style="color:blue;">t</span>


<!-- badges: start -->
<!-- badges: end -->

A small repository for spectral data of happy little fluorochromes.

```{r spectrum, echo = FALSE}
library(ggplot2)
spec <- vroom::vroom(gzfile("spectra.tsv.gz"), show_col_types = F) |> dplyr::filter(fluorochrome == "PE-Dazzle594")
maxes <- vroom::vroom("em_ex_maxima.tsv", show_col_types = F)
pp <- ggplot(spec |>
         tidyr::pivot_longer(cols = c(em, ex), names_to = "type", values_to = "value") |>
         tidyr::drop_na(), aes(x = nm, y = value)) +
  geom_line(aes(linetype = type), color = "white") + # colrr::col_pal("material")[1]
  colrr::theme_material(bg_color = "#0D1117") +
  theme(legend.position.inside = c(0.95,0.9), legend.key.size = ggplot2::unit(0, "pt"),
        legend.key.spacing.y = ggplot2::unit(10, "pt")) +
  labs(linetype = NULL, y = "norm intensity [%]", title = "PE-Dazzle594") +
  geom_segment(data = dplyr::filter(maxes, fluorochrome == "PE-Dazzle594"), aes(x = nm, y = 0, yend = norm_intensity, linetype = type), color = "white") +
  guides(linetype = guide_legend(position = "inside", label.position = "bottom"))
```

```{r, echo=FALSE}
pp
```

See plots of excitation and emission spectra in spectra_images.

All raw data for those are in spectra.tsv.gz and em_ex_maxima.tsv.

```{r, echo=FALSE}
print(knitr::kable(spec |> tidyr::drop_na() |> dplyr::slice_head(n = 10)))
print(knitr::kable(dplyr::filter(maxes, fluorochrome == "PE-Dazzle594")))

#dplyr::filter(maxes, fluorochrome == "PE-Dazzle594")# |> gt::gt()
```

Peaks were detected by algorithm. This may either be oversensitive and detect too many of them or miss some. Plots were checked and only very few minor peaks are not detected.
In very few spectra lowest emission peak is below lowest excitation which should not be according to [Stokes shift](https://en.wikipedia.org/wiki/Stokes_shift). Some spectra include negative values or values above 100 which is weird but data was left as obtained in this case. However, leading and trailing zeros were removed for instance.



